Supplementary Materials- A Bayesian networks approach to infer social changes in burials in northeastern Taiwan during the European colonization period

### 2021-05-12 analysis/paper/paper.Rmd
moved figure 6 from the main text to the SI

```{r figure-bgof-two-phases, fig.cap = "Goodness-of-fit diagnostics for the pre-European model (top) and the post-European model (below). Boxplots represent distributions calculated on 100 network graphs simulated from the estimated posterior distribution. Red lines represent distributions of observed networks, and gray lines show the 95% intervals."}
library(magick)
pre_bgof_img <- image_read(here::here("analysis/figures/003-pre-bgof.png"))
post_bgof_img <- image_read(here::here("analysis/figures/004-post-bgof.png"))
image_append(c(pre_bgof_img, post_bgof_img), stack = T)
```

<!--assessment of MCMC analysis and BGOF--> 
Our computational models reproduce networks that resemble the structural features of our observed networks. Bayesian goodness of fit diagnostics plots (Figure \@ref(fig:figure-bgof-two-phases); details in Supplementary Online Materials) demonstrate that both models fit the observed networks very well for the minimum geodesic distance distribution (i.e. the number of edges between node pairs in a shortest path, @Hunter2008) and the degree distribution. For edgewise shared partner distribution, despite some observations falling outside the 95% interval, the fit is generally good with most observations within it. We also compared the first three distribution moments of each observed distribution and their corresponding simulated distributions, represented by means. Figure \@ref(fig:figure-distribution-moments) shows that modeled values from the pre-European network are slightly closer to the observed values for the mean and the variance of distributions, compared to the values from the post-European network. In general, this demonstrates a slightly better fit between model and data for the pre-European network.

>>>>

<!--assessment of MCMC analysis and BGOF--> 
Our computational models reproduce networks that resemble the structural features of our observed networks according to Bayesian goodness of fit diagnostics (details in Supplementary Online Materials), showing both models fit the observed networks very well. We also compared the first three distribution moments of each observed distribution and their corresponding simulated distributions, represented by means. Figure \@ref(fig:figure-distribution-moments) shows that modeled values from the pre-European network are slightly closer to the observed values for the mean and the variance of distributions, compared to the values from the post-European network. In general, this demonstrates a slightly better fit between model and data for the pre-European network.

### 2021-05-12 analysis/paper/supplementary-material.Rmd
moved figure 6 from the main text to the SI

Our Bayesian GOF diagnostics, shown in the main text, summarized three distributions, including degree, minimum geodesic distance, and edgewise shared partner distributions. This provides a statistical approach to check how well the estimated posterior parameter distribution, based on our hypotheses, can reproduce networks with similar general structural features of the observed networks. We then compared the distribution of our observed networks, the networks before and after the arrival of Europeans, with the distribution of our hypothesized models. We expect to see the models fit with our hypotheses, indicative of an increased social inequality after the foreign contact. In addition, the covariates can give some more clues for the underlying mechanisms for the formations of each network, such as the relative importance of age and sex.

@@

>>>>

@@

Our Bayesian GOF diagnostics summarized three distributions, including degree, minimum geodesic distance, and edgewise shared partner distributions. The diagnostics plots (Figure \@ref(fig:figure-bgof-two-phases)) demonstrate that both models fit the observed networks very well for the minimum geodesic distance distribution (i.e. the number of edges between node pairs in a shortest path, @Hunter2008) and the degree distribution. For edgewise shared partner distribution, despite some observations falling outside the 95% interval, the fit is generally good with most observations within it. This provides a statistical approach to check how well the estimated posterior parameter distribution, based on our hypotheses, can reproduce networks with similar general structural features of the observed networks. We then compared the distribution of our observed networks, the networks before and after the arrival of Europeans, with the distribution of our hypothesized models. We expect to see the models fit with our hypotheses, indicative of an increased social inequality after the foreign contact. In addition, the covariates can give some more clues for the underlying mechanisms for the formations of each network, such as the relative importance of age and sex.

```{r figure-bgof-two-phases, fig.cap = "Goodness-of-fit diagnostics for the pre-European model (top) and the post-European model (below). Boxplots represent distributions calculated on 100 network graphs simulated from the estimated posterior distribution. Red lines represent distributions of observed networks, and gray lines show the 95% intervals."}
library(magick)
pre_bgof_img <- image_read(here::here("analysis/figures/003-pre-bgof.png"))
post_bgof_img <- image_read(here::here("analysis/figures/004-post-bgof.png"))
image_append(c(pre_bgof_img, post_bgof_img), stack = T)
```
